---
title: "Code Book for Getting and Cleaning Data Course Project"
author: "lactobacillusnut"
date: "30/05/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Difference with original dataset

The dataset to be analysed is downloaded from:

<https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip>  
\  

The companion site for the dataset can be accessed from:

<http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones>
\  

Although there are no major changes to the variable names, the Table 1 below will summarise the abbreviations used in the variable names in the final output file *"avgbyparticipant.txt"*. An indication of *NA* signifies no changes to the orginal abbreviations or absence in the original dataset.


```{r table-simple, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
require(pander)
panderOptions('table.split.table', Inf)
set.caption("Summary of variable abbrevations")
my.data <- " Original | Modified | Meaning
  *NA*          | ID        | Participant/Subject ID from subject_test.txt or subject_train.txt
  *NA*          | Activity  | Activity labels from activity_labels.txt
  f             | *NA*      | Frequency Domain           
  t             | *NA*      | Time Domain, 50Hz
  -XYZ          | XYZ       | Denotes 3-axial signals in X, Y, or Z directions
  Acc           | *NA*      | Accelerometer readings
  Gyro          | *NA*      | Gyroscope readings
  Body          | *NA*      | Denotes Acc or Gyro readings by the Body
  Gravity       | *NA*      | Denotes Acc or Gyro readings due to Gravity
  Jerk          | *NA*      | Denotes the derived Jerk signal 
  Mag           | *NA*      | Denotes the magnitude
  mean()        | Mean      | Indicates a mean calculation
  std()         | Std       | Indicates a standard deviation calculation"
df <- read.delim(textConnection(my.data),header=FALSE,sep="|",strip.white=TRUE,stringsAsFactors=FALSE)
names(df) <- unname(as.list(df[1,])) # put headers on
df <- df[-1,] # remove first row
row.names(df)<-NULL
pander(df, style = 'rmarkdown')
```